---
title: "Practicing with Quarto"
author: "Eric Friedlander"
format: html
---

# Introduction

Blash heres my intro

# Data Cleaning

## Package Loading

Today, we're going to analyze some data on flights from New York City!!! Let's first load some packages. We're going to need the folloinwg packages:

- `tidyverse`: This includes all of the functions for manipulating and plotting our data
- `nycflights13`: This includes the data set that we're working with

```{r}
#| message: false
# install.packages(c("tidyverse", "nycflights13"))
library(dplyr)
library(ggplot2)
library(nycflights13)
```

Now that we've loaded the datasets, let's create some exploratory plots. The plot below shows us that Jetblue (coded as `B6`) is the most common airline to leave out of JFK.

## Exploring JFK

```{r}
flights |> 
    filter(origin == "JFK") |> 
    ggplot(aes(x = carrier)) +
    geom_bar()
```

### Finding the most common airline

```{r}
#| include: false
top_airline <- flights |> 
    count(carrier) |> 
    slice_max(n, n=1) |> 
    pull(carrier)
```

The top airline is `r top_airline`.

The way calculate the mean is $\frac{\sum x_i}{n}$